**The status of the microbial census: an update**

### 2015-12-04 doc/notebook/Archaeal_data_acquisition.Rmd
Fix problem from reading in strings as factors

```{r emirge_metadata}
emirge_metadata <- read.table(file="data/raw/emirge.metadata", row.names=1)
archaea_sequences <- read.table(file="data/mothur/emirge.archaea.taxonomy")[1]
archaea_emirge_metadata <- emirge_metadata[archaea_sequences$V1,]

>>>>

```{r emirge_metadata}
emirge_metadata <- read.table(file="data/raw/emirge.metadata", row.names=1)
archaea_sequences <- read.table(file="data/mothur/emirge.archaea.taxonomy", stringsAsFactors=FALSE)[1]
archaea_emirge_metadata <- emirge_metadata[archaea_sequences$V1,]
